The all-seeing eye of resonant Auger electron spectroscopy: a study on aqueous KCl

### 2018-02-14 suppinfo.tex
feb 14 (kolya's corrections included)
Kolya's corrections are included, several things left for D. to correct

\newcommand{\tsveta}[1]{\textcolor{red}{#1}}
\newcommand{\nico}[1]{\textcolor{red}{#1}}
\newcommand{\kolya}[1]{\textcolor{blue}{#1}}
\newcommand{\denis}[1]{\textcolor{green}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Tsveta Miteva}
\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}

\author{Nikolai Kryzhevoi}
\affiliation{Theoretische Chemie, Physikalisch-Chemisches Institut, Universit\"at Heidelberg, Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}

@@

\author{Wandared Pokapanich}
\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000 Thailand}

\author{Th. Saisopa}
\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}

\author{P. Songsiriritthigul}
\affiliation{NANOTEC-SUT Center of Excellence on Advanced Functional Nanomaterials and School of Physics,
Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}

\author{Y. Rattanachai}
\affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}

\author{Andreas Dreuw}
\affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}

\author{Jan Wenzel}
\affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}

@@

\author{Gunnar \"{O}hrwall}
\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}

@@

\author{Jean-Pascal Rueff}
\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
\affiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}

@@

\begin{figure}
\centering
\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}. The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step. From these curves we determine the charge transfer time $\tau_{\texttt{CT}}$ according to the formula $\tau_{\texttt{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.  The green line defines the Cl$^{-}_{\texttt{aq}}$(1s) ionization potential.}
\label{fg:si_ct_time}
\end{figure}

>>>>

\newcommand{\tsveta}[1]{\textcolor{red}{#1}}
\newcommand{\denis}[1]{\textcolor{green}{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Meta-data block
%% ---------------
%% Each author should be given as a separate \author command.
%%
%% Corresponding authors should have an e-mail given after the author
%% name as an \email command. Phone and fax numbers can be given
%% using \phone and \fax, respectively; this information is optional.
%%
%% The affiliation of authors is given after the authors; each
%% \affiliation command applies to all preceding authors not already
%% assigned an affiliation.
%%
%% The affiliation takes an option argument for the short name.  This
%% will typically be something like "University of Somewhere".
%%
%% The \altaffiliation macro should be used for new address, etc.
%% On the other hand, \alsoaffiliation is used on a per author basis
%% when authors are associated with multiple institutions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{Tsveta Miteva}
\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
\email{tsveta.miteva@upmc.fr}

\author{Nikolai V. Kryzhevoi}
\affiliation{Theoretische Chemie, Physikalisch-Chemisches Institut, Universit\"at Heidelberg, Im Neuenheimer Feld 229, D-69120 Heidelberg, Germany}

@@

\author{Wandared Pokapanich}
\affiliation{Faculty of Science, Nakhon Phanom University, Nakhon Phanom 48000, Thailand}
%
\author{Thanit Saisopa}
\author{Prayoon Songsiriritthigul}
\affiliation{School of Physics, Suranaree University of Technology, Nakhon Ratchasima 30000, Thailand}
%
\author{Yuttakarn Rattanachai}
\affiliation{Department of Applied Physics, Faculty of Sciences and Liberal Arts, Rajamangala University of Technology Isan, Nakhon Ratchasima 30000, Thailand}

\author{Andreas Dreuw}
\author{Jan Wenzel}
\affiliation{Interdisciplinary Center for Scientific Computing, Ruprecht-Karls University, Im Neuenheimer Feld 205A, D-69120 Heidelberg, Germany}

@@

\author{Gunnar \"{O}hrwall}
\affiliation{MAX IV Laboratory, Lund University, P.O. Box 118, SE-22100 Lund, Sweden}

@@

\author{Jean-Pascal Rueff}
\affiliation{Sorbonne Universit\'{e}, CNRS, Laboratoire de Chimie Physique Mati\`{e}re et Rayonnement, UMR 7614, F-75005 Paris, France}
\alsoaffiliation{Synchrotron SOLEIL, l`Orme des Merisiers, Saint-Aubin, F-91192 Gif-sur-Yvette Cedex, France}

@@

\begin{figure}
\centering
\includegraphics[scale=0.9]{figures/partial_cross_sec_ct_time.pdf}
\caption{Partial cross sections and charge transfer time extracted from Fig.\ \ref{fg:2dmap_cl}. The blue and red curves are obtained by integrating the area of the 2p$^{-2}$ and 2p$^{-2}$4p final states ($^1$D state region only) at each photon energy step. From these curves we determine the charge transfer time $\tau_{\text{CT}}$ according to the formula $\tau_{\text{CT}} = \tau l/d$, with $\tau$ being the Cl 1s core-hole lifetime and $l/d$ being the intensity ratio of the localized (2p$^{-2}$ 4p) and delocalized (2p$^{-2}$) states at a given excitation energy \cite{foehlisch05:373}.  The green line defines the Cl$^{-}_{\text{aq}}$(1s) ionization potential.}
\label{fg:si_ct_time}
\end{figure}
